### 2016-12-23 trunk/docs/intro.tex
VERSION 0.6.0
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@3067 40876441-3496-0410-a613-a2fca35b2ae2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  intro.tex
%
%  Contains introduction and quick start for users.
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  (c) 2016 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Code releases may be downloaded via anonymous download
\begin{lstlisting}[style=terminalverbatim]
http://ccpforge.cse.rl.ac.uk/gf/project/ludwig/frs/
\end{lstlisting}
The current release is available as \texttt{ludwig-0.4.0.tar.gz}.
Alternatively, registered users can obtain the code via svn checkout
in the same way as developers.

@@

%\paragraph{Parallel: }
\textbf{Parallel: }
The executable compiled and linked against the MPI library can
be run with the MPI launcher for the local system, often
\texttt{mpirun}. For example, a run on 8 MPI tasks produces a
similar output to that seen in the serial case, but reports
details of the local domain decomposition:
\begin{lstlisting}
$ mpirun -np 8 ./Ludwig.exe ./serial-auto-c01.inp
Welcome to Ludwig v0.1.26 (MPI version running on 8 processes)
...
System details
--------------
System size:    64 64 64
Decomposition:  2 2 2
Local domain:   32 32 32
...
\end{lstlisting}
The decomposition is controlled by the \texttt{grid} key in
the input. Here, \texttt{grid 2\_2\_2} is consistent with the
8 MPI tasks specified on the command line, and the resulting
local decomposition is 32 lattice points in each coordinate direction.
If no grid is specified in the input, or a request is
make for a grid which cannot be met (e.g., the product
of the grid dimensions does not agree with the total number
of MPI tasks available)
the code will try to determine its own decomposition as best
it can. If no valid parallel decomposition is available at all,
the code will exit with a message to that effect.

@@

Output for colloidal particle data is again to file with a name encoding
the time step and parallel docomposition of the output. For example,
\begin{lstlisting}
bash-3.2$ ls config*
config.cds00000020.001-001
\end{lstlisting}
contains particle data for time step 20 in a format described ELSEWHERE.
These data may be requested in ASCII or raw binary format.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  intro.tex
%
%  Contains introduction and quick start for users.
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  (c) 2016-2017 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Code releases may be downloaded via anonymous download
\begin{lstlisting}[style=terminalverbatim]
http://ccpforge.cse.rl.ac.uk/gf/project/ludwig/frs/
\end{lstlisting}
The current release is available as \texttt{ludwig-0.6.0.tar.gz}.
Alternatively, registered users can obtain the code via svn checkout
in the same way as developers.

@@

\textbf{Parallel: }
The executable compiled and linked against the MPI library can
be run with the MPI launcher for the local system, often
\texttt{mpirun}. For example, a run on 8 MPI tasks produces a
similar output to that seen in the serial case, but reports
details of the local domain decomposition:
\begin{lstlisting}
$ mpirun -np 8 ./Ludwig.exe ./serial-auto-c01.inp
Welcome to Ludwig v0.1.26 (MPI version running on 8 processes)
...
System details
--------------
System size:    64 64 64
Decomposition:  2 2 2
Local domain:   32 32 32
...
\end{lstlisting}
The decomposition is controlled by the \texttt{grid} key in
the input. Here, \texttt{grid 2\_2\_2} is consistent with the
8 MPI tasks specified on the command line, and the resulting
local decomposition is 32 lattice points in each coordinate direction.
If no grid is specified in the input, or a request is
make for a grid which cannot be met (e.g., the product
of the grid dimensions does not agree with the total number
of MPI tasks available)
the code will try to determine its own decomposition as best
it can. If no valid parallel decomposition is available at all,
the code will exit with a message to that effect.

@@

Output for colloidal particle data is again to file with a name encoding
the time step and parallel decomposition of the output. For example,
\begin{lstlisting}
bash-3.2$ ls config*
config.cds00000020.001-001
\end{lstlisting}
contains particle data for time step 20 in a format described in
Section~\ref{examples}.
These data may be requested in ASCII or raw binary format.
